Reproduction of \"Who Does Voter ID Keep from Voting?\" by Bernard L. Fraga and Michael G. Miller (2022)

### 2024-02-15 paper/SSRP/reproduction_paper.qmd
Updated reproduction paper

```{r}
#| label: fig-a3
#| fig-cap: General Impediments of Texas voters who filed RIDs in 2016 by Race (Figure A3 from paper)
#| echo: false # Code will run and its output will show but the code itself will not be included in the doc
#| warning: false # Warnings are not included 
#| message: false # Messages are not included 
# Graph
# Referenced code from https://r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html
# To figure out how to sort 
combined_figure_A3_data |>
  mutate(reasons = fct_reorder(reasons, desc(percent))) |>
  ggplot(mapping = aes(x = reasons, y = percent)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  labs(
    x = "Reasons",
    y = "Percent"
  ) +
  coord_flip() + 
  # Referenced code from https://github.com/tidyverse/ggplot2/issues/2762
  # to figure out how to put labels on the left and use facet_grid
  facet_grid(vars(race), switch = "y") +
  guides(x = guide_axis(angle = 0), ) +
  theme(plot.title = element_text(size = 9, face = "bold"),
        axis.title=element_text(size = 9, face = "bold")) + 
  ggtitle("General Impediments of Texas voters who filed RIDs in 2016 by Race")
```

```{r}
#| label: tbl-a3
#| tbl-cap: General Impediments of Texas voters who filed RIDs in 2016 by Race (Figure A3 from paper)
#| echo: false # Code will run and its output will show but the code itself will not be included in the doc
#| warning: false # Warnings are not included 
#| message: false # Messages are not included

>>>>

```{r}
#| label: fig-a3
#| fig-cap: General impediments of Texas voters who filed RIDs with "Other" option selected in 2016 by Race (Figure A3 from paper)
#| echo: false # Code will run and its output will show but the code itself will not be included in the doc
#| warning: false # Warnings are not included 
#| message: false # Messages are not included 
# Graph
# Referenced code from https://r-graph-gallery.com/267-reorder-a-variable-in-ggplot2.html
# To figure out how to sort 
combined_figure_A3_data |>
  mutate(reasons = fct_reorder(reasons, desc(percent))) |>
  ggplot(mapping = aes(x = reasons, y = percent)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  labs(
    x = "Reasons",
    y = "Percent"
  ) +
  coord_flip() + 
  # Referenced code from https://github.com/tidyverse/ggplot2/issues/2762
  # to figure out how to put labels on the left and use facet_grid
  facet_grid(vars(race), switch = "y") +
  guides(x = guide_axis(angle = 0), ) +
  theme(plot.title = element_text(size = 9, face = "bold"),
        axis.title=element_text(size = 9, face = "bold")) + 
  ggtitle("General Impediments of Texas voters who filed RIDs in 2016 by Race")
```

```{r}
#| label: tbl-a3
#| tbl-cap: General impediments of Texas voters who filed RIDs with "Other" option selected in 2016 by Race (Figure A3 from paper)
#| echo: false # Code will run and its output will show but the code itself will not be included in the doc
#| warning: false # Warnings are not included 
#| message: false # Messages are not included
